\vspace{1.0cm} \LARGE \bf MERS-CoV spillover at the camel-human interface

### 2017-08-07 mers-structure.tex
Updating AR's affiliations and grants

\author[1]{Gytis Dudas}
\author[2]{Luiz Max Carvalho}
\author[2,3,4]{Andrew Rambaut}
\author[1]{Trevor Bedford}

\affil[1]{Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center, Seattle, WA, USA}
\affil[2]{Institute of Evolutionary Biology, University of Edinburgh, Edinburgh, UK}
\affil[3]{Fogarty International Center, National Institutes of Health, Bethesda, MD, USA}
\affil[4]{Centre for Immunology, Infection and Evolution at the University of Edinburgh, Edinburgh, UK}

@@

\section*{Acknowledgements}
We would like to thank Allison Black for useful discussion and advice.
GD is supported by the Mahan postdoctoral fellowship from the Fred Hutchinson Cancer Research Center.
TB is a Pew Biomedical Scholar and is supported by NIH R35 GM119774-01.
We gratefully acknowledge the contribution of the following scientists for sharing MERS-CoV sequence data before publication:

>>>>

\author[1]{Gytis Dudas}
\author[2]{Luiz Max Carvalho}
\author[2,3]{Andrew Rambaut}
\author[1]{Trevor Bedford}

\affil[1]{Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center, Seattle, WA, USA}
\affil[2]{Institute of Evolutionary Biology, University of Edinburgh, Edinburgh, UK}
\affil[3]{Fogarty International Center, National Institutes of Health, Bethesda, MD, USA}

@@

\section*{Acknowledgements}
We would like to thank Allison Black for useful discussion and advice.
GD is supported by the Mahan postdoctoral fellowship from the Fred Hutchinson Cancer Research Center.
TB is a Pew Biomedical Scholar and is supported by NIH R35 GM119774-01.
AR was supported in part by the European Union Seventh Framework Programme for research, technological development and demonstration under Grant Agreement no. 278433-PREDEMICS and no. 725422-RESERVOIRDOCS, and the Wellcome Trust through project 206298/Z/17/Z.
MAS is partly supported by NSF grant DMS 1264153 and NIH grants R01 HG006139 and R01 AI107034.
We gratefully acknowledge support from NVIDIA Corporation with the donation of parallel computing resources used for this research.

We gratefully acknowledge the contribution of the following scientists for sharing MERS-CoV sequence data before publication:
